Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-14 paper/ms.tex
updating sparse benchmark

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin_default.pdf}
\caption{Benchmark\figurelabel{benchmark}}
\end{center}
\end{figure}

>>>>

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin.pdf}
\caption{A benchmark showing the computational scaling of the \celerite\
    implementation as a function of the number of data points and the number
    of terms.
    (left) The cost of computing \eq{gp-likelihood}
    \figurelabel{benchmark}}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin_lapack.pdf}
\caption{Benchmark\figurelabel{benchmark-lapack}}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin_sparse.pdf}
\caption{Benchmark\figurelabel{benchmark-sparse}}
\end{center}
\end{figure}
